SULI Report!

### 2015-08-20 doc/suli-report-swe.tex
Added a (temporary) CPU per lightcone bar graph in the results section. #81
Rewrote the Computational Performance section of the SULI report to account for the new CPU figure. #81

A secondary goal of this research was to investigate how quickly the prediction for the shear and convergence for a single background source could be made. The mean CPU time required for the prediction per lightcone was ${80\pm10}$ ms for the first run. However, many small improvements to the coding infastructure of \texttt{Pangloss} were made to speed up the prediction. The average CPU time for a lensing prediction per lightcone after various changes is plotted in Figure \ref{cpu_plot}.

%************************
(CPU time per lightcone plot)\\
%************************
(Include RAM in plot??)

>>>>

A secondary goal of this research was to investigate how quickly the prediction for the shear and convergence for a single background source could be made. The mean CPU time required for the prediction per lightcone was ${80\pm10}$ ms for the first run. However, many small improvements to the coding infastructure of \texttt{Pangloss} were made to speed up the prediction. The average CPU time for a lensing prediction per lightcone for four separate runs after various (and cumulative) changes is plotted in Figure \ref{cpu_plot}. Run 1 corresponds to the original \texttt{Pangloss} framework code, run 2 only wrote the needed quantities for this analysis to the catalog \texttt{astropy} tables, run 3 changed the redshift grid binning to be done once for all halos in the drilling rather than for every individual halo in lensing, and run 4 optimized various lensing calculations with matrices whenever possible. Cumulatively, these changes alone accounted for a 70\% decrease in mean CPU time per lightcone and halved the initial variation.

%% Mean lightcone CPU time
\begin{figure}
    \centering
    \includegraphics[width=0.475\textwidth]{figs-swe/profile_bar.png}
    \captionsetup{justification=raggedright,singlelinecheck=false}
    \caption{The mean CPU runtime per lightcone for various runs with different (and cumulative) code optimizations described in the text. The cumulative changes account for a 70\% decrease in the mean CPU time and a halving of the variation.}
    \label{cpu_plot}
\end{figure}
